A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-11-05 paper/paper.tex
paper: fix bugs in msc, get title/author/abstract in paper

  On another side, it is known that semi-simplicial and semi-cubical sets are related to iterated Reynolds's parametricity, respectively in its unary and binary variants\dots

  We exploit this correspondence to develop a uniform indexed definition of both augmented semi-simplicial and semi-cubical sets, which is additionally fully formalized in Coq's dependent type theory. Beside the interest in the construction itself, we expect it to eventually serve as models of type theory preserving more definitional equalities than presheaf models do.
\end{abstract}
\begin{keywords}
  simplicial set, cubical set, coq, formalization, HoTT
\end{keywords}
% \maketitle

>>>>

  It is known that semi-simplicial and semi-cubical sets are related to iterated Reynolds's parametricity, respectively in its unary and binary variants\dots

  We exploit this correspondence to develop a uniform indexed definition of both augmented semi-simplicial and semi-cubical sets, which is additionally fully formalized in Coq's dependent type theory. Beside the interest in the construction itself, we expect it to eventually serve as models of type theory preserving more definitional equalities than presheaf models do.
\end{abstract}
\begin{keywords}
  simplicial set, cubical set, coq, formalization, HoTT
\end{keywords}
\maketitle
